\textbf{Traffic Analysis} \\ {\Large\itshape A write-up}

### 2019-03-12 paper.tex
Add files via upload
conclusion almost

The default gateway 10.0.0.2 broadcasted asking for the compromised host. The broadcast was made 485 times. This could possibly indicate the command and control server attempting to reestablish communication with the target, as the default gateway attempted to ARB probe for the host. This assumes that the network has no firewall in place, or one that is misconfigured. Since packets entering the network should be blocked unless they are solicited from inside the network, as part of an on going connection. Thus the best explanation for the anomalous ARP probes are that the C2 server is checking whether his compromised hosts are still online.

@@

>>>>

The default gateway 10.0.0.2 broadcasted asking for the compromised host. The broadcast was made 485 times. This could possibly indicate the command and control server attempting to reestablish communication with the target, as the default gateway attempted to ARB probe for the host. This assumes that the network has no firewall in place, or one that is misconfigured. Since packets entering the network should be blocked unless they are solicited from inside the network, as part of an on going connection. Thus the best explanation for the anomalous ARP probes are that the C2 server is checking whether his compromised host are still online.

@@

The network traffic analysis uncovered the behavior over the wire of a host infected by a strain of ransomware known as Maktub. The host exhibited signs of compromise following interaction with a mail server, indicating a malicious mail attachment was the initial point of entry. The host established a openVPN session tunneled over TLS as a likely secure communication channel to the C2. Finally, in order to provide a payment platform for victim, TOR hidden services over a .onion to the web link.
